% vim: shiftwidth=2:tabstop=2:softtabstop=2:expandtab:textwidth=120:colorcolumn=120
\documentclass{llncs}
%\documentclass[llncs]{IEEEtran}

\usepackage{microtype} %This gives MUCH better PDF results!
%\usepackage[active]{srcltx} %DVI search
\usepackage[cmex10]{amsmath}
\usepackage{amssymb}
\usepackage{fnbreak} %warn for split footnotes
\usepackage{url}
%\usepackage{qtree} %for drawing trees
%\usepackage{fancybox} % if we need rounded corners
%\usepackage{pict2e} % large circles can be drawn
%\usepackage{courier} %for using courier in texttt{}
%\usepackage{nth} %allows to \nth{4} to make 1st 2nd, etc.
%\usepackage{subfigure} %allows to have side-by-side figures
%\usepackage{booktabs} %nice tables
%\usepackage{multirow} %allow multiple cells with rows in tabular
\usepackage[utf8]{inputenc} % allows to write Faugere correctly
\usepackage[bookmarks=true, citecolor=black, linkcolor=black, colorlinks=true]{hyperref}
\hypersetup{
pdfauthor = {Vijay Ganesh, Trevor Hansen, Dan Liew, Ryan Govostes, Khoo Yit Phang, Mate Soos},
pdftitle = {STP},
pdfsubject = {SMT Competition 2015},
pdfkeywords = {SMT Solver},
pdfcreator = {PdfLaTeX with hyperref package},
pdfproducer = {PdfLaTex}}
%\usepackage{butterma}

%\usepackage{pstricks}
%\usepackage{graphicx,epsfig,xcolor}
%\usepackage[algoruled, linesnumbered, lined]{algorithm2e} %algorithms
\setlength{\parskip}{1ex}
\begin{document}
\title{STP}
\author{Vijay Ganesh, Trevor Hansen, Dan Liew, Ryan Govostes, Khoo Yit Phang, Mate Soos}
\institute{}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

\section{Introduction}
STP\cite{Vijay:Thesis:2007} is an efficient open source solver for QF\_BV and arrays without extensionality. STP
recursively simplifies bit-vector constraints, solves linear bit-vector equations, and then eagerly encodes them to CNF
for solving. Array axioms are added as needed during an abstraction-refinement phase.

Two versions of STPs are submitted to STMCOMP 2015. Both are  revision bff0edecbb7c08a of STP's publicly available source code
repository~\cite{STP:github}. The version with "-minisat-v15" uses MiniSat~\cite{MiniSat:github} revision
37dc6c67 set as default solver. The verison with "-cryptominisat4-v15" contains CryptoMiniSat4~\cite{CMS:github}
revision 24db9219b180 set as default solver.

\section{Development history}
STP was originally developed by Vijay Ganesh under the supervision of Professor David Dill. Later releases were
developed by Trevor Hansen under the supervision of Peter Schachte and Harald Søndergaard. STP handles arbitrary
precision integers using Steffen Beyer's library. STP encodes into CNF via the and-inverter graph package ABC of Alan
Mishchenko~\cite{Brayton:2010:AAI:2144310.2144317}.

Since SMT-COMP 2015 we have made great progress at cleaning up the STP repository and have significantly
improved the underlying SAT solver, CryptoMiniSat4's performance. The STP repository now contains a large number of
automated testing, buliding and deployment scripts. Further, it contains a large test suite and more inner self-checks
through asserts. STP is being actively developed on \href{https://github.com/stp/stp}{GitHub}.

\section*{Acknowledgements}
We would like to thank everyone who submitted bug reports, pull requests, and other useful data such as test cases.

\bibliographystyle{splncs}
\bibliography{sigproc}

\vfill
\pagebreak

\end{document}
